---
title: 'Data analysis for 4-methyl phenol from digestate experiments'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Plots

```{r}
ggplot(dat, aes(time.end, fmp, colour = treatment, group = interaction(tunnel, treatment))) +
  geom_line() +
  geom_point() +
  facet_wrap(~ experiment)
```

# Stats

Set reference to untreatmented cattle manure.

Unit of analysis will be wind tunnel plot.

First fit model to each wind tunnel to get the ks.

Look at fit.

```{r}
ggplot(dat, aes(time.end, fmp, colour = treatment, group = interaction(tunnel, treatment))) +
  geom_line() +
  geom_point() +
  geom_line(aes(time.end, fmp.calc), lty = '11') +
  facet_wrap(~ experiment)
```

Take a look at km values.

```{r}
ggplot(lmods, aes(experiment, km, fill = treatment)) +
  geom_boxplot()
```

Now analysis.

```{r}
modk1 <- lm(km ~ treatment * experiment, data = lmods)
summary.aov(modk1)
summary(modk1)
```

Interactions complicated.
Let's look by experiment.
First experiment 1.

```{r}
modexp1 <- aov(km ~ treatment, data = lmods, subset = experiment == 'Experiment 1')
summary(modexp1)
summary.lm(modexp1)
coef(modexp1)
confint(modexp1)
model.tables(modexp1, type = 'means')
```

**Use this model in paper.**
Both D-CM and CC-CM have lower k than reference in experiment 1.

Experiment 2 next.

```{r}
modexp2 <- aov(km ~ treatment, data = lmods, subset = experiment == 'Experiment 2')
summary(modexp2)
summary.lm(modexp2)
coef(modexp2)
confint(modexp2)
model.tables(modexp2, type = 'means')
```

Both D-CM and CC-CM have lower k than reference in experiment 2.
**Use this model in paper for experiment 2.**

Diagnostic plots.

```{r}
plot(modexp1, ask = FALSE)
```

```{r}
plot(modexp2, ask = FALSE)
```

Not terrible.

Now initial flux.

```{r}
modf1 <- aov(log10(fmp) ~ experiment * treatment, data = d1)
summary(modf1)
summary.lm(modf1)
100 * (1 - 10^coef(modf1))
100 * (1 - 10^confint(modf1))
```
