---
title: 'Data analysis for digestate experiments'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# NH3 plots

```{r}
ggplot(dat, aes(exper, e.rel, fill = treat)) +
  geom_boxplot() +
  ylim(0, 25)
```

# NH3 stats

Set reference to untreated cattle manure.

```{r}
dat$treat <- factor(dat$treat, levels = c('U-CM', 'CC-CM', 'D-CM'))
dat$exper <- factor(dat$exper)
```

First model, with interaction, no transformation.

```{r}
m1 <- aov(e.rel ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

Without interaction.

```{r}
m2 <- aov(e.rel ~ treat + exper, data = dat)
summary(m2)
summary.lm(m2)
```

**This model is the one we should use in the paper.**
Diagnostic plots look better, and the boxplot above shows smaller differences for experiment 2 (not larger as expected if there were a fixed relative effect).

```{r}
m3 <- aov(log10(e.rel) ~ treat * exper, data = dat)
summary(m3)
```

```{r}
m4 <- aov(log10(e.rel) ~ treat + exper, data = dat)
summary(m4)
summary.lm(m4)
```

CC-CM and D-CM are clearly different.
But neither is clearly different from the reference.
Makes interpretation just a bit tricky but not terrible.
Some evidence of a difference but presumably digestion pH effect is moderated by low DM, and variability was high, so power is low.

Check diagnostic plots.

```{r}
plot(m1, ask = FALSE)
```

Diagnostic plots with transformation.

```{r}
plot(m4, ask = FALSE)
```

Actually looks better without the transformation.

# OAV plots

```{r}
ggplot(dat, aes(exper, oav, fill = treat)) +
  geom_boxplot() 
```

# OAV stats

```{r}
m1 <- aov(oav ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

```{r}
m2 <- aov(log10(oav) ~ treat * exper, data = dat)
summary(m2)
summary.lm(m2)
```

Quite interesting.
Interaction drops out.

```{r}
m3 <- aov(log10(oav) ~ treat + exper, data = dat)
summary(m3)
summary.lm(m3)
confint(m3)
```

**This is the model we should use in the paper.**
Most importantly (I think) the boxplot shows that a relative effects concept fits better than absolute effects.
And diagnostic plots are better with the transformation.
Lastly, the interaction drops out, which is simpler and so better by some perspectives.

Look at back-transformed results.
These are relative reductions in % of reference.

```{r}
100 * (1 - 10^coef(m3))
100 * (1 - 10^confint(m3))
```

So we conclude CC-CM is lower, but D-CM difference isn't clear.

Check diagnostic plots.

```{r}
plot(m1, ask = FALSE)
```

Diagnostic plots with transformation.

```{r}
plot(m3, ask = FALSE)
```

# SOAV plots

```{r}
ggplot(dat, aes(exper, soav, fill = treat)) +
  geom_boxplot() 
```

# SOAV stats

```{r}
m1 <- aov(soav ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

Transform.

```{r}
m2 <- aov(log10(soav) ~ treat * exper, data = dat)
summary(m2)
summary.lm(m2)
```

We lose the interaction again.


```{r}
m3 <- aov(log10(soav) ~ treat + exper, data = dat)
summary(m3)
summary.lm(m3)
confint(m3)
```

Look at back-transformed results.
These are relative reductions in % of reference.

```{r}
100 * (1 - 10^coef(m3))
100 * (1 - 10^confint(m3))
```

So we conclude both CC-CM and D-CM are lower.

Check residuals.

```{r}
plot(m3, ask = FALSE)
```





