---
title: 'Data analysis of cumulative NH3 for digestate experiments'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# NH3 plots

```{r}
ggplot(dat, aes(exper, e.rel, fill = treat)) +
  geom_boxplot() +
  ylim(0, 25)
```

# NH3 stats

Set reference to untreated cattle manure.

```{r}
dat$treat <- factor(dat$treat, levels = c('U-CM', 'CC-CM', 'D-CM'))
dat$exper <- factor(dat$exper)
```

First model, with interaction, no transformation.

```{r}
m1 <- aov(e.rel ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

Without interaction.

```{r}
m2 <- aov(e.rel ~ treat + exper, data = dat)
summary(m2)
summary.lm(m2)
```

**This model is the one we should use in the paper.**
Diagnostic plots look better, and the boxplot above shows smaller differences for experiment 2 (not larger as expected if there were a fixed relative effect).

```{r}
m3 <- aov(log10(e.rel) ~ treat * exper, data = dat)
summary(m3)
```

```{r}
m4 <- aov(log10(e.rel) ~ treat + exper, data = dat)
summary(m4)
summary.lm(m4)
```

CC-CM and D-CM are clearly different.
But neither is clearly different from the reference.
Makes interpretation just a bit tricky but not terrible.
Some evidence of a difference but presumably digestion pH effect is moderated by low DM, and variability was high, so power is low.

Check diagnostic plots.

```{r}
plot(m1, ask = FALSE)
```

Diagnostic plots with transformation.

```{r}
plot(m4, ask = FALSE)
```

Actually looks better without the transformation.
