---
title: 'Data analysis for odor from digestate experiments'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# Plots

```{r}
ggplot(dat, aes(time, oav, colour = treat, group = interaction(rep, treat))) +
  geom_line() +
  geom_point() +
  facet_wrap(~ exper)
```

```{r}
ggplot(dat, aes(time, log10(oav), colour = treat, group = interaction(rep, treat))) +
  geom_line() +
  geom_point() +
  facet_wrap(~ exper)
```

Looks linear enough.

```{r}
ggplot(dat, aes(time, log(oav), colour = treat, group = interaction(rep, treat))) +
  geom_line(alpha = 0.2) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE) +
  facet_wrap(~ exper)
```

# Stats

So, our question will be (referring to last plot above) "are there differences in slope and initial value?".
I had expected to use the intercept and slope terms in the analysis, but the least-squares lines don't fit very well in all cases at the start.
And anyway, the initial measurements are our best estimate of initial OAV.

Set reference to untreated cattle manure.

```{r}
dat$treat <- factor(dat$treat, levels = c('U-CM', 'CC-CM', 'D-CM'))
dat$exper <- factor(dat$exper)
```

Unit of analysis will be wind tunnel plot.

First fit linear model to each wind tunnel to get the slopes.

```{r}
lmods <- dat[, .(int = coef(lm(log(oav) ~ time))[1], 
                 slope = coef(lm(log(oav) ~ time))[2]), 
             by = .(exper, treat, rep)]
```

Take a look at slopes.

```{r}
ggplot(lmods, aes(exper, slope, fill = treat)) +
  geom_boxplot()
```

Clear differences for D-CM in both experiments, but no difference for CC-CM in experiment 2.

Now analysis.

Look at slope.

```{r}
modslope1 <- lm(slope ~ treat * exper, data = lmods)
summary.aov(modslope1)
summary(modslope1)
```

Interactions complicated.
Let's look by experiment.
First experiment 1.

```{r}
modexp1 <- aov(slope ~ treat, data = lmods, subset = exper == 'Experiment 1')
summary(modexp1)
summary.lm(modexp1)
coef(modexp1)
confint(modexp1)
model.tables(modexp1, type = 'means')
```

**Use this model in paper.**
Both D-CM and CC-CM have lower slope than reference in experiment 1.
Results are a first-order constant with units of 1/hr that describes the drop in flux over time.
Note that `log()` (not `log10()`) used above gives this result.

Experiment 2 next.

```{r}
modexp2 <- aov(slope ~ treat, data = lmods, subset = exper == 'Experiment 2')
summary(modexp2)
summary.lm(modexp2)
coef(modexp2)
confint(modexp2)
model.tables(modexp2, type = 'means')
```

Here only D-CM is lower, and the effect seems larger than in experiment 1.
**Use this model in paper for experiment 2.**

Diagnostic plots.

```{r}
plot(modexp1, ask = FALSE)
```

```{r}
plot(modexp2, ask = FALSE)
```

Not terrible.

Now look at first measurement period in lieu of intercept.

Add interval number to data.

```{r}
dat <- dat[, int := as.integer(factor(time)), by = exper]
```

And take a look at the initial OAV values.

```{r}
dd <- subset(dat, int == 1)
ggplot(dd, aes(exper, oav, fill = treat)) +
  geom_boxplot()
```

Check transformed values.

```{r}
ggplot(dd, aes(exper, log10(oav), fill = treat)) +
  geom_boxplot()
```

See CC-CM lower in both experiments, D-CM lower in experiment 2 only.

```{r}
modinit1 <- aov(log10(oav) ~ treat * exper, data = dat, subset = int == 1)
summary(modinit1)
```
Drop interaction.

```{r}
modinit2 <- aov(log10(oav) ~ treat + exper, data = dat, subset = int == 1)
summary(modinit2)
summary.lm(modinit2)
100 * (1 - 10^coef(modinit2))
100 * (1 - 10^confint(modinit2))
100 * (10^coef(modinit2))
100 * (10^confint(modinit2))
```

**Use this model in paper.**
Back-transformed coef and confint results give % reduction relative to reference.
CC-CM clearly lower, D-CM not.

Check diagnostic plots.

```{r}
plot(modinit2, ask = FALSE)
```

These look good.
