---
title: 'Data analysis for digestate experiments'
output: pdf_document
author: Sasha D. Hafner
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

# NH3 plots

```{r}
ggplot(dat, aes(exper, e.rel, colour = treat)) +
  geom_jitter(height = 0)
```

```{r}
ggplot(dat, aes(as.integer(factor(exper)), e.rel, colour = treat, group = interaction(treat, rep))) +
  geom_point() +
  geom_line()
```

```{r}
ggplot(dat, aes(exper, e.rel, fill = treat)) +
  geom_boxplot() +
  ylim(0, 25)
```

# NH3 stats

Set reference to untreated cattle manure.

```{r}
dat$treat <- factor(dat$treat, levels = c('U-CM', 'CC-CM', 'D-CM'))
dat$exper <- factor(dat$exper)
```

```{r}
m1 <- aov(e.rel ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

No need to look at interaction.


```{r}
m2 <- aov(e.rel ~ treat + exper, data = dat)
summary(m2)
summary.lm(m2)
```

CC-CM and D-CM are clearly different.
But neither is clearly different from the reference.
Makes interpretation just a bit tricky.
Some evidence of a difference but presumably digestion pH effect is moderated by low DM, and variability was high, so power is low.

Check residuals.

```{r}
plot(m1, ask = FALSE)
```

Looks fine, no need to transform.

# OAV plots

```{r}
ggplot(dat, aes(exper, oav, colour = treat)) +
  geom_jitter(height = 0)
```

```{r}
ggplot(dat, aes(as.integer(factor(exper)), oav, colour = treat, group = interaction(treat, rep))) +
  geom_point() +
  geom_line()
```

```{r}
ggplot(dat, aes(exper, oav, fill = treat)) +
  geom_boxplot() 
```

# OAV stats

```{r}
m1 <- aov(oav ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
confint(m1)
```

For OAV there is a clear interaction.
D-CM is no different from the reference in the first experiment, but is in the second.
The apparent CC-CM reduction is also larger in experiment 2.

Check residuals.

```{r}
plot(m1, ask = FALSE)
```

No obviously improved with a transformation, but let's try log anyway to for fixed relative effects.

```{r}
m2 <- aov(log10(oav) ~ treat * exper, data = dat)
summary(m2)
summary.lm(m2)
```

Quite interesting.
Interaction drops out.

```{r}
m3 <- aov(log10(oav) ~ treat + exper, data = dat)
summary(m3)
summary.lm(m3)
confint(m3)
```

Look at back-transformed results.
These are relative reductions in % of reference.

```{r}
100 * (1 - 10^coef(m3))
100 * (1 - 10^confint(m3))
```

So we conclude CC-CM is lower, but D-CM difference isn't clear.

Check residuals.

```{r}
plot(m3, ask = FALSE)
```

# SOAV plots

```{r}
ggplot(dat, aes(exper, soav, colour = treat)) +
  geom_jitter(height = 0)
```

```{r}
ggplot(dat, aes(as.integer(factor(exper)), soav, colour = treat, group = interaction(treat, rep))) +
  geom_point() +
  geom_line()
```

```{r}
ggplot(dat, aes(exper, soav, fill = treat)) +
  geom_boxplot() 
```

# SOAV stats

```{r}
m1 <- aov(soav ~ treat * exper, data = dat)
summary(m1)
summary.lm(m1)
```

Transform.

```{r}
m2 <- aov(log10(soav) ~ treat * exper, data = dat)
summary(m2)
summary.lm(m2)
```

We lose the interaction again.


```{r}
m3 <- aov(log10(soav) ~ treat + exper, data = dat)
summary(m3)
summary.lm(m3)
confint(m3)
```

Look at back-transformed results.
These are relative reductions in % of reference.

```{r}
100 * (1 - 10^coef(m3))
100 * (1 - 10^confint(m3))
```

So we conclude both CC-CM and D-CM are lower.

Check residuals.

```{r}
plot(m3, ask = FALSE)
```





